---
title: Trend of Non Working Population in Australia
author: Echo
date: 2021-11-15T09:00:00
slug: []
categories: []
meta_img: images/image.png
description: Description for the page
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

##### The aging population has risen, while the percentage of young people has remained the same. This would gradually form an 'inverted pyramid' population structure. We need to be alert to this demographic problem. This is because it may result in low productivity, insufficient labor supply, and financial health system burdens. At the same time, the increase in the number of retirees would cause their savings to be withdrawn, accelerating the decline in the total savings of an economy. Additionally, a low-productive working population would lead to a decline in economic output and aggravate the decline in income levels and investment from domestic and foreign markets (UN report 2019). Most of these issues have a direct or indirect negative impact on economic development.

```{r}
library(plotly) 
library(tidyverse)

population = read.csv("state.csv")
population = population %>% 
    filter(LABEL == "Australia") %>% 
    mutate(`Under 15` = X0.14,
           `Working Population` = Working) %>% 
    mutate(`Over 64` = 100 - `Under 15` - `Working Population`) %>% 
    mutate(YEAR = as.factor(YEAR))
# population = population %>% 
#     select(YEAR, `Under 14`, `Working Population`, `Over 64`) %>% 
#     pivot_longer(`Under 14`:`Over 64`, names_to = "group") %>% 
#     filter(group != "Working Population")
```


```{r}
fig <- plot_ly(population, x = ~YEAR, y = ~`Under 15`, type = 'bar', name = 'Under 15', text = ~`Under 15`, textposition = 'auto')
fig <- fig %>% add_trace(y = ~`Over 64`, name = 'Over 64', text = ~`Over 64`, textposition = 'auto') 
fig <- fig %>%
  layout(showlegend = T,
         xaxis = list(title = 'Year'), 
         yaxis = list(title = 'Percent (%)'),
         legend = list(orientation = "h",   # show entries horizontally
                     xanchor = "center",  # use center of legend as anchor
                     x = 0.8))

fig
```

<div class="alert alert-light" role="alert" style="width:100%">
Data source: Australian Bureau of Statistics 2011-2016.

Source: UN report 2019, ‘ABOUT AGING POPULATION-PROBLEMS & SOLUTIONS’.
</div>
