---
title: GDP Growth history in Australia
author: Echo
date: 2021-11-15T11:00:00
slug: []
categories: []
meta_img: images/image.png
description: Description for the page
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

##### During these recent two decades, Australia's GDP growth rate has basically shown a downward trend. In particular, it encountered a pandemic lockdown in 2020. The Australian authorities have even adopted the strictest epidemic lockdown, such as banning outdoor sports and dog walking (Arora 2020). This obviously has a negative impact on economic development.

```{r}
library(tidyverse)
library(plotly)

gdp = read.csv("GDP.csv", skip = 4)
gdp = gdp %>% select(1,2,5:65) %>% pivot_longer(cols = X1960:X2020, names_to='year', values_to='gdp')
gdp = gdp %>% 
    filter(Country.Name == "Australia") %>% 
    mutate(year = as.numeric(str_extract(year, "[0-9]+"))) %>% 
    arrange(year)
```

```{r}
options(warn = -1)
fig <- plot_ly(gdp, type = 'scatter', mode = 'lines')%>%
  add_trace(x = ~year, y = ~gdp, name = '', line=list(color='blue'))%>%
  layout(showlegend = F,
         xaxis = list(title = 'Year'), 
         yaxis = list(title = 'GDP growth (annual %)'))

fig <- fig %>%
  layout(
         plot_bgcolor='#ffff')

fig
```


<div class="alert alert-light" role="alert" style="width:100%">
Data source: World Bank Data, https://data.worldbank.org/indicator/NY.GDP.MKTP.KD.ZG, accessed 8 November 2021.

Source: Arora A 2020, ‘Australia Imposes 'world's Toughest' COVID Lockdown; Outdoor Exercise, Dog-walking Banned’, Republic World, accessed 9 November 2021.
</div>