---
title: Trend of Working Population in Australia
author: Echo
date: 2021-11-15T10:00:00
slug: []
categories: []
meta_img: images/image.png
description: Description for the page
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

##### While Australia's GDP growth rate fluctuates to a certain extent, it maintains a downward trend. This is because the economic development in 2011 may have been affected by the aftermath of the 2008 financial crisis. The 2008 financial crisis had a profound impact on Australian residents in both economic and social dimensions. Specifically, changes in subjective well-being and financial pressure restrained their desire to consume (Saunders & Wong 2011). Note that the working population in Australia is also showing a downward trend. 

```{r}
library(highcharter) 
library(tidyverse)
library(xts)

population = read.csv("state.csv")
names(population)[3] = "percent"
population = population %>% 
    filter(LABEL == "Australia")

gdp = read.csv("GDP.csv", skip = 4)
gdp = gdp %>% select(1,2,5:65) %>% pivot_longer(cols = X1960:X2020, names_to='year', values_to='gdp')
gdp = gdp %>% 
    mutate(year = as.numeric(str_extract(year, "[0-9]+"))) %>% 
    filter(Country.Name == "Australia") %>% 
    rename(LABEL = Country.Name, YEAR = year)
```

```{r}
dat = inner_join(population %>% select(LABEL, YEAR, percent),
              gdp %>% select(LABEL, YEAR, gdp))
dat$YEAR = as.factor(dat$YEAR)
```

```{r}
hchart(dat, hcaes(x = YEAR), type="line") %>%
    hc_yAxis_multiples(list(title = list(text = "GDP Growth (%)"), opposite = FALSE),
                       list(showLastLabel = FALSE, opposite = TRUE, title = list(text = "Working population (%)"))) %>% 
    hc_add_series(dat[, "gdp"], yAxis = 0, showInLegend = TRUE, name = "GDP Growth (%)") %>% 
    hc_add_series(dat[, "percent"], yAxis = 1, showInLegend = TRUE, name = "Working population (%)")
```


<div class="alert alert-light" role="alert" style="width:100%">
Data source: Australian Bureau of Statistics 2011-2016.

Source: Saunders P & Wong M 2011, ‘The social impact of the global financial crisis in Australia’, The Australian journal of social, pp. 291-309, DOI:10.1002/j.1839-4655.2011.tb00220.x.
</div>