---
title: Trend of Non Working population in Australia by State
author: Echo
date: 2021-11-15T07:00:00
slug: []
categories: []
meta_img: images/image.png
description: Description for the page
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

##### In the end, we analyze the actual situation of the population structure of each state. In terms of younger generation, the decline in the Northern Territory and Tasmania is the most obvious. This is what we need to pay attention to.

##### Overall, population aging is the only way for developed countries. However, we need to care about and control population issues because of the close relationship between population and economy. You can consider Robinson story at the beginning. A reasonable increase in the population will create more demand to improve people's lives in the future.


```{r}
library(plotly) 
library(tidyverse)

population = read.csv("state.csv")
population = population %>% 
    filter(LABEL != "Australia") %>% 
    mutate(`Under 15` = X0.14,
           `Working Population` = Working) %>% 
    mutate(`Over 64` = 100 - `Under 15` - `Working Population`) %>% 
    mutate(YEAR = as.factor(YEAR))
population1 = population %>% 
    select(LABEL, YEAR, `Under 15`) %>% 
    pivot_wider(names_from = LABEL, values_from = `Under 15`)
population2 = population %>% 
    select(LABEL, YEAR, `Over 64`) %>% 
    pivot_wider(names_from = LABEL, values_from = `Over 64`)
```


#### Under 15

```{r}
options(warn = -1)
fig <- plot_ly(population1, x = ~YEAR, y = ~`New South Wales`, name = "New South Wales", type = 'scatter', mode = 'lines') 

for (n in names(population1)[3:9]) {
    fig = fig %>% add_trace(y = population1[[n]], name = n, mode = 'lines+markers')
}

fig <- fig %>%
  layout(showlegend = T,
         xaxis = list(title = 'Year'), 
         yaxis = list(title = 'Working age population (%)'),
         legend = list(orientation = "h",   # show entries horizontally
                     xanchor = "center",  # use center of legend as anchor
                     x = 0.5, y=-0.2))

fig
```


#### Over 64

```{r}
options(warn = -1)
fig <- plot_ly(population2, x = ~YEAR, y = ~`New South Wales`, name = "New South Wales", type = 'scatter', mode = 'lines') 

for (n in names(population2)[3:9]) {
    fig = fig %>% add_trace(y = population2[[n]], name = n, mode = 'lines+markers')
}

fig <- fig %>%
  layout(showlegend = T,
         xaxis = list(title = 'Year'), 
         yaxis = list(title = 'Working age population (%)'),
         legend = list(orientation = "h",   # show entries horizontally
                     xanchor = "center",  # use center of legend as anchor
                     x = 0.5, y=-0.2))

fig
```


<div class="alert alert-light" role="alert" style="width:100%">
Data source: Australian Bureau of Statistics 2011-2016.
</div>